---
title: "Data424 Final"
author: "Connor"
date: "11/27/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
rm(list = ls(all.names = TRUE))
```

```{r}
#packages
library(tidyr)
library(dplyr)
library(leaps)
library(psych)
library(ggplot2)
library(MASS)
```

```{r}
ames = read.csv("House.csv")
```

```{r}
ames = ames %>% tidyr::replace_na(list(BsmtQual = "none", BsmtCond = "none", BsmtExposure="none", 
                                       BsmtFinType1="none",BsmtFinType2="none", FireplaceQu="none", 
                                       GarageQual="none", GarageCond="none", PoolQC="none",Fence="none",
                                       MiscFeature="none", Alley="none", GarageType="none",GarageFinish="none",
                                       GarageYrBlt=round(mean(ames$GarageYrBlt, na.rm=TRUE))))
```

```{r}
ames2 = ames %>% drop_na()
```

```{r}
ames2 = as.data.frame(unclass(ames2), stringsAsFactors = TRUE)
factors = sapply(ames2, is.factor)
str(ames2)
```

```{r}
lmames_orig = lm(SalePrice~MSSubClass++LotFrontage+LotArea+as.numeric(Neighborhood)+
              OverallQual +OverallCond+YearBuilt+as.numeric(RoofMatl)+
            as.numeric(MasVnrType)+MasVnrArea+as.numeric(ExterQual)+as.numeric(BsmtQual)+
              as.numeric(BsmtExposure)+TotalBsmtSF+GrLivArea+BsmtFullBath+
              BedroomAbvGr+as.numeric(KitchenQual)+TotRmsAbvGrd+as.numeric(Functional)+
              Fireplaces+GarageCars+WoodDeckSF+ScreenPorch+PoolArea+
              as.numeric(PoolQC)+as.numeric(SaleCondition), data=ames2)
summary(lmames_orig)
```

```{r}
#aic_ames_orig = step(lmames_orig, k=2)
aic_ames_log_orig = step(lmames_orig, k=log(1194))
```

```{r}
b_orig = regsubsets(SalePrice~MSSubClass++LotFrontage+LotArea+as.numeric(Neighborhood)+
            OverallQual +OverallCond+YearBuilt+as.numeric(RoofMatl)+
            as.numeric(MasVnrType)+MasVnrArea+as.numeric(ExterQual)+as.numeric(BsmtQual)+
            as.numeric(BsmtExposure)+TotalBsmtSF+GrLivArea+BsmtFullBath+
            BedroomAbvGr+as.numeric(KitchenQual)+TotRmsAbvGrd+as.numeric(Functional)+
            Fireplaces+GarageCars+WoodDeckSF+ScreenPorch+PoolArea+
            as.numeric(PoolQC)+as.numeric(SaleCondition), data=ames2)
summary(b_orig)$adjr2
```

```{r}
lmames = lm(SalePrice~MSSubClass+LotFrontage+LotArea+as.numeric(Neighborhood)+
              OverallQual+YearBuilt+as.numeric(RoofMatl)+
              MasVnrArea+as.numeric(ExterQual)+as.numeric(BsmtQual)+
              as.numeric(BsmtExposure)+TotalBsmtSF+GrLivArea+BsmtFullBath+
              BedroomAbvGr+as.numeric(KitchenQual)+as.numeric(Functional)+
              Fireplaces+GarageCars+ScreenPorch+
              as.numeric(SaleCondition), data=ames2)
summary(lmames)
```

```{r}
aic_ames = step(lmames, k=2)
aic_ames_log = step(lmames, k=log(1194))
anova(aic_ames_log)
```

```{r}
lmames2 = lm(SalePrice~MSSubClass++LotFrontage+LotArea+as.numeric(Neighborhood)+
              OverallQual+YearBuilt+as.numeric(RoofMatl)+
              MasVnrArea+as.numeric(ExterQual)+as.numeric(BsmtQual)+
              as.numeric(BsmtExposure)+GrLivArea+
              BedroomAbvGr+as.numeric(KitchenQual)+as.numeric(Functional)+
              Fireplaces+GarageCars+ScreenPorch+
              as.numeric(SaleCondition), data=ames2)
summary(lmames2)
```

```{r}
aic_ames2 = step(lmames2, k=2)
aic_ames_log2 = step(lmames2, k=log(1194))
anova(aic_ames2)
anova(aic_ames_log2)
```

```{r}
b = regsubsets(SalePrice~MSSubClass+LotFrontage+LotArea+as.numeric(Neighborhood)+OverallQual+
              YearBuilt+as.numeric(RoofMatl)+MasVnrArea+as.numeric(ExterQual)+
              as.numeric(BsmtQual)+as.numeric(BsmtExposure)+GrLivArea+BedroomAbvGr+
              as.numeric(KitchenQual)+as.numeric(Functional)+Fireplaces+GarageCars+
              ScreenPorch+as.numeric(SaleCondition), data=ames2)
summary(b)
summary(b)$adjr2
```

```{r}
lmames3 = lm(SalePrice~as.numeric(BsmtQual)+as.numeric(BsmtExposure)+
              as.numeric(KitchenQual)+GarageCars+GrLivArea+MSSubClass+
              OverallQual+YearBuilt+MasVnrArea, data=ames2)
summary(lmames3)
```


```{r}
lmames4 = lm(SalePrice~BsmtQual+BsmtExposure+
              KitchenQual+GarageCars+GrLivArea+MSSubClass+
              OverallQual+YearBuilt+MasVnrArea, data=ames2)
summary(lmames4)
```

```{r}
b2 = regsubsets(SalePrice~as.numeric(BsmtQual)+as.numeric(BsmtExposure)+
              as.numeric(KitchenQual)+GarageCars+GrLivArea+MSSubClass+
              OverallQual+YearBuilt+MasVnrArea, data=ames2)
summary(b2)
summary(b2)$cp
summary(b2)$adjr2
```

```{r}
aic_ames3 = step(lmames3, k=2)
aic_ames_log3 = step(lmames3, k=log(1194))
anova(aic_ames3)
anova(aic_ames_log3)
```

All variables used and meanings:
BsmtExposure: Refers to walkout or garden level walls. 5 grade scale
BsmtQual: Evaluates the height of the basement. 6 grade scale
KitchenQual: Kitchen quality. 5 grade scale
GarageCars: Size of garage in car capacity
GrLivArea: Above grade (ground) living area square feet
MSSubClass: Identifies the type of dwelling involved in the sale
OverallQual: Rates the overall material and finish of the house. 10 grade scale
YearBuilt: Original construction date 
MasVnrArea: Masonry veneer area in square feet. Seems to be another way to measure square footage

```{r}
cor_numeric = cor(ames2$MasVnrArea, ames2$GrLivArea)
print(cor_numeric)
qplot(MasVnrArea, GrLivArea, data=ames2)
```

```{r}
chi1 = table(ames2$BsmtQual, ames2$BsmtExposure)
chisq.test(chi1)

chi2 = table(ames2$BsmtQual, ames2$KitchenQual)
chisq.test(chi2)

chi3 = table(ames2$BsmtQual, ames2$GarageCars)
chisq.test(chi3)

chi4 = table(ames2$BsmtQual, ames2$MSSubClass)
chisq.test(chi4)

chi5 = table(ames2$BsmtQual, ames2$YearBuilt)
chisq.test(chi5)

chi6 = table(ames2$BsmtQual, ames2$OverallQual)
chisq.test(chi6)

chi7 = table(ames2$BsmtExposure, ames2$KitchenQual)
chisq.test(chi7)

chi8 = table(ames2$BsmtExposure, ames2$GarageCars)
chisq.test(chi8)

chi9 = table(ames2$BsmtExposure, ames2$OverallQual)
chisq.test(chi9)

chi10 = table(ames2$BsmtExposure, ames2$YearBuilt)
chisq.test(chi10)

chi11 = table(ames2$BsmtExposure, ames2$MSSubClass)
chisq.test(chi11)

chi12 = table(ames2$KitchenQual, ames2$GarageCars)
chisq.test(chi12)

chi13 = table(ames2$KitchenQual, ames2$MSSubClass)
chisq.test(chi13)

chi14 = table(ames2$KitchenQual, ames2$OverallQual)
chisq.test(chi14)

chi15 = table(ames2$KitchenQual, ames2$YearBuilt)
chisq.test(chi15)

chi16 = table(ames2$GarageCars, ames2$MSSubClass)
chisq.test(chi16)

chi17 = table(ames2$GarageCars, ames2$OverallQual)
chisq.test(chi17)

chi18 = table(ames2$GarageCars, ames2$YearBuilt)
chisq.test(chi18)

chi19 = table(ames2$MSSubClass, ames2$OverallQual)
chisq.test(chi19)

chi20 = table(ames2$MSSubClass, ames2$YearBuilt)
chisq.test(chi20)

chi21 = table(ames2$OverallQual, ames2$YearBuilt)
chisq.test(chi21)
```



```{r}
lmFullSignificant = lm(SalePrice~MSSubClass + MSZoning + LotFrontage + LotArea + Alley + LotShape + LandContour +  LotConfig + Neighborhood + Condition1 + BldgType + HouseStyle + OverallQual + OverallCond + YearBuilt + RoofStyle + RoofMatl + MasVnrType + MasVnrArea + ExterQual + BsmtQual + BsmtExposure + BsmtFinType1 + BsmtUnfSF + TotalBsmtSF + LowQualFinSF + GrLivArea + BsmtFullBath + FullBath + BedroomAbvGr + KitchenAbvGr + KitchenQual + TotRmsAbvGrd + Functional + Fireplaces + GarageCars + WoodDeckSF + ScreenPorch + PoolArea + PoolQC + SaleCondition, data = ames2 )
summary(lmFullSignificant)
```


Plots
```{r}
plot(lmames3)
```

```{r}
qplot(GrLivArea, SalePrice, data=ames2)
cor(ames2$SalePrice, ames2$GrLivArea)
qplot(MasVnrArea, SalePrice, data=ames2)
cor(ames2$SalePrice, ames2$MasVnrArea)
qplot(YearBuilt, SalePrice, data=ames2)
```

